---
title: "yli130_Assignment 3"
author: "Yanxi Li"
date: "10/9/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create & Solve Model 

```{r}
# using the library
library(lpSolveAPI)

# set the working directory
setwd("C:/Users/yanxi/OneDrive - Kent State University/Desktop/Quantitative Management Modeling/Assignment")

# read the lp file which has the formulation in it
lprec <- read.lp("Weight.lp")

# solve the model
solve(lprec)

# get maximum profit
get.objective(lprec)

# each decision variable's value
get.variables(lprec)
```

## Reduced Cost

```{r cars}
get.sensitivity.obj(lprec) # get reduced cost

# get range bottom line
get.sensitivity.obj(lprec)$objfrom

# get range upper line
get.sensitivity.obj(lprec)$objtill
```

Reduced cost value is shown in the next shadow price dual part.

## Shadow Price

```{r}
get.sensitivity.rhs(lprec)  # get shadow price / dual solution

# get shadow price value (the first 11 value)
get.sensitivity.rhs(lprec)$duals

# get range bottom line
get.sensitivity.rhs(lprec)$dualsfrom

# get range upper line
get.sensitivity.rhs(lprec)$dualstill
```
As shown above, dual value is 0, 0, 0, 12, 20, 60, 0, 0, 0, -0.08, 0.56, 0, 0, -24, -40, 0, 0, -360, -120, 0.
Dual value is mixed with shadow price and reduced cost.

The first 11 is shadow price value which is 0, 0, 0, 12, 20, 60, 0, 0, 0, -0.08, 0.56.

THe last 9 is reduce price value which is 0, 0, -24, -40, 0, 0, -360, -120, 0.

## Range of Reduced Cost

Here I am trying to build a data-frame which can show the results clearly.
```{r}

# build 3 columns
Plant_Size <- c("Plant1_Large", "Plant1_Medium", "Plant1_Small", "Plant2_Large", 
                              "Plant2_Medium", "Plant2_Small", "Plant_3_Large", 
                                                    "Plant3_Medium", "Plant3_Small")

Reduce_Cost_Bottom <- c(3.60e+02, 3.45e+02, -1.00e+30, -1.00e+30, 
                                      3.45e+02, 2.52e+02, -1.00e+30, -1.00e+30, 2.04e+02)

Reduce_Cost_Upper <- c(4.60e+02, 4.20e+02, 3.24e+02, 4.60e+02, 4.20e+02, 
                                                  3.24e+02, 7.80e+02, 4.80e+02, 1.00e+30)

# build data-frame
Reduce_Cost_Range <- data.frame(Plant_Size, Reduce_Cost_Bottom, Reduce_Cost_Upper)

# show Reduced Cost Range results
Reduce_Cost_Range
```

## Range of Shadow Price

Similar as the Reduced Cost shows above.
```{r}

# build 3 columns
Constraints <- c("Constraint_1", "Constraint_2", "Constraint_3", "Constraint_4", "Constraint_5", 
                                 "Constraint_6", "Constraint_7", "Constraint_8", "Constraint_9", 
                                                                   "Constraint_10", "Constraint_11")

Shadow_Price_Bottom <- c(-1e+30, -1e+30, -1e+30, 1.122222e+04, 1.15e+04, 4.8e+03, -1e+30,
                                                         -1e+30, -1e+30, -2.5e+04, -1.25e+04)

Shadow_Price_Upper <- c(1e+30, 1e+30, 1e+30, 1.388889e+04, 1.25e+04, 5.181818e+03, 1e+30,
                                                                  1e+30, 1e+30, 2.5e+04, 1.25e+04)
# build data-frame
Shadow_Price_Range <- data.frame(Constraints, Shadow_Price_Bottom, Shadow_Price_Upper)

# show Shadow Price Range results
Shadow_Price_Range
```

## Formualte Dual and Solve

```{r}
# formulate the duals in the lp file
lprec_new <- read.lp("Assign3.lp")

# solve the dual model
solve(lprec_new)

# get dual optimal solution
get.objective(lprec_new)

# get dual decision variables
get.variables(lprec_new)
```
According to the above result, dual model optimal solution is the same as primal model, and dual model's decision variables' value is exactly the primal model's shadow price value.















